---
title: "Technical Interview"
subtitle: "Internship Data Science"
format: html
editor: source
editor_options: 
  chunk_output_type: console
---

# Part 1

## Task 1

When storing data in spreadsheets, it is recommended to store dates as YYYY-MM-DD. Why?

## Task 2 (max 5 minutes)

You are working on a paper about sanitation facilities and you are setting up a new directory structure for this project. 

1. Locate the "Files" tab in the RStudio IDE where the files and directories of this project are displayed.

2. Use the RStudio IDE graphical user interface (GUI) to create a new directory titled "sanitation-facilities".

3. Open the "sanitation-facilities" directory.

4. Inside the "sanitation-facilities" directory, use the RStudio IDE GUI to create a directory structure that stores:

- unprocessed raw data
- processed data
- code
- text

# Part 2

## Task 1

The collection of tidyverse R Packages is installed in your computing environment. 

1. Run the R code chunk below to execute the code and load the R Packages.

```{r}

library(tidyverse)

```

## Task 2

The file at what-a-waste-city-level-data.csv contains a dataset on solid waste management from around the world. The data has 5 variables (columns) with one observation (row) for each city with reported data.

The first five variables are:

- The name of the city that reported data.
- The country where the city that reported data is located.
- The income category by the World Bank that is associated with the country.
- The population of each city.
- The municipal solid waste generation in tons per year

1. Execute the R code in the R code chunk below.

2. Inspect the R code and describe verbally, line by line, what the code does.

```{r}

waste_city <- read_csv("what-a-waste-city-level-data.csv") |>
  mutate(income_id = factor(income_id, 
                            levels = c("HIC", "UMC", "LMC", "LIC")))

```

3. Execute the R code in the R code chunk below.

4. Inspect the R code and describe verbally, line by line, what the code does.

```{r}
waste_city |> 
  group_by(income_id) |> 
  summarise(
    count = n()
  )
```

## Task 3

Use the `waste_city` object and write R code to answer the following questions: 

1. How many cities are represented in this dataset? 

2. How many countries are represented in this dataset? 

3. How many countries have reported data for five cities or more? 

```{r}

```

## Task 4

Use the `waste_city` object and write R code to complete the following task:

1. Prepare a box plot with income category on the x-axis and municipal solid waste generation in tons per year on the y-axis. 

2. Describe the elements of the boxplot verbally. What does the thick line represent? What does the box represent? What do the whiskers represent?

3. Transform the y-axis to a base 10 logarithmic scale.

4. Rename the x- axis to "Income Category" and the y-axis to "MSW Generation (tons/year)"

```{r}

```

## Task 5

Write R code to solve the following tasks

1. Read what-a-waste-country-level-data.csv and remove rows containing any NAs, assigining the result to a new tibble (dataframe) called waste_country

2. Read gdp-data.csv and assign to a tibble (dataframe) called gdp

3. Use a left join to combine the waste_country and gdp tibbles using the ISO country code variable columns for matches

4. Prepare a scatterplot for GDP and municipal solid waste generation.

5. Describe how you could improve this plot.


```{r}



```


